A non-contextual hidden variable model for quantum mechanics

### 2017-02-08 finalPaper.tex
- ‘.#finalPaper.tex’ / ‘finalPaper.tex’

In this letter we have presented
non-multiplicativity as an alternative to
contextuality and as an essential signature of
quantumness at the kinematic level.  We expect
this to provide new insights that will be useful
in the areas of foundations of QM and QIP.
Implications of quantum dynamics for
our model and in general for the notion of
non-multiplicativity need to be explored
further to assess accuracy of contextuality.
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{acknowledgments} ASA and Arvind acknowledge
funding from KVPY and DST Grant No.
EMR/2014/000297 respectively.
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\end{acknowledgments}
%\bibliographystyle{apsrev4-1}
\bibliography{references} \end{document}

>>>>

In this letter we have presented
non-multiplicativity as an alternative to
contextuality and as an essential signature of
quantumness at the kinematic level. {\color{red} Our result
emphasises the importance of quantum dynamics
to the discussion of contextuality which may have
implications on our model and in general on the
notion of non-multiplicativity.}
%Implications of quantum dynamics for
%our model and in general for the notion of
%non-multiplicativity need to be explored
%further.
We expect this to provide new insights that will be useful
in the areas of foundations of QM and QIP.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{acknowledgments} ASA and Arvind acknowledge
funding from KVPY and DST Grant No.
EMR/2014/000297 respectively.
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\end{acknowledgments}
%\bibliographystyle{apsrev4-1}
\bibliography{references} \end{document}
